treats manual

### 2023-05-25 inst/gitbook/07_specific_examples.Rmd
manual header change

---
title: "Specific examples"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
# bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "treats manual"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
# bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

### 2023-05-25 inst/gitbook/_book/treats_manual.tex
manual header change

  pdftitle={Specific examples},

@@

\title{Specific examples}
\author{Thomas Guillerme (\href{mailto:guillert@tcd.ie}{\nolinkurl{guillert@tcd.ie}})}
\date{2023-05-25}

@@

\begin{verbatim}
## $main
## $main$A
## $main$A$process
## function (x0 = 0, edge.length = 1, Sigma = diag(length(x0)), 
##     ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = Sigma * edge.length, 
##         ...)))
## }
## <bytecode: 0x55b094e15a20>
## <environment: namespace:treats>
## 
## $main$A$start
## [1] 0
## 
## $main$A$trait_id
## [1] 1
## 
## 
## 
## $background
## NULL
\end{verbatim}

@@

\begin{verbatim}
## $waiting
## $waiting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(rexp(1, sum(lineage$n * (bd.params$speciation + bd.params$extinction))))
## }
## <bytecode: 0x55b093879f20>
## <environment: namespace:treats>
## 
## $waiting$internal
## NULL
## 
## 
## $selecting
## $selecting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(sample(lineage$n, 1))
## }
## <bytecode: 0x55b093879270>
## <environment: namespace:treats>
## 
## $selecting$internal
## NULL
## 
## 
## $speciating
## $speciating$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(runif(1) < (bd.params$speciation/(bd.params$speciation + 
##         bd.params$extinction)))
## }
## <bytecode: 0x55b09387f640>
## <environment: namespace:treats>
## 
## $speciating$internal
## NULL
## 
## 
## $call
## $call$waiting
## $call$waiting$fun
## [1] "default"
## 
## 
## $call$selecting
## $call$selecting$fun
## [1] "default"
## 
## 
## $call$speciating
## $call$speciating$fun
## [1] "default"
\end{verbatim}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpwcuuU8/file55f335659f38}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpwcuuU8/file55f34d5ddce7}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpwcuuU8/file55f3254da0ed}

>>>>

  pdftitle={treats manual},

@@

\title{treats manual}
\author{Thomas Guillerme (\href{mailto:guillert@tcd.ie}{\nolinkurl{guillert@tcd.ie}})}
\date{2023-05-25}

@@

\begin{verbatim}
## $main
## $main$A
## $main$A$process
## function (x0 = 0, edge.length = 1, Sigma = diag(length(x0)), 
##     ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = Sigma * edge.length, 
##         ...)))
## }
## <bytecode: 0x55b3b2541d88>
## <environment: namespace:treats>
## 
## $main$A$start
## [1] 0
## 
## $main$A$trait_id
## [1] 1
## 
## 
## 
## $background
## NULL
\end{verbatim}

@@

\begin{verbatim}
## $waiting
## $waiting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(rexp(1, sum(lineage$n * (bd.params$speciation + bd.params$extinction))))
## }
## <bytecode: 0x55b3b0f93c78>
## <environment: namespace:treats>
## 
## $waiting$internal
## NULL
## 
## 
## $selecting
## $selecting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(sample(lineage$n, 1))
## }
## <bytecode: 0x55b3b0f9bdc8>
## <environment: namespace:treats>
## 
## $selecting$internal
## NULL
## 
## 
## $speciating
## $speciating$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(runif(1) < (bd.params$speciation/(bd.params$speciation + 
##         bd.params$extinction)))
## }
## <bytecode: 0x55b3b0f9b498>
## <environment: namespace:treats>
## 
## $speciating$internal
## NULL
## 
## 
## $call
## $call$waiting
## $call$waiting$fun
## [1] "default"
## 
## 
## $call$selecting
## $call$selecting$fun
## [1] "default"
## 
## 
## $call$speciating
## $call$speciating$fun
## [1] "default"
\end{verbatim}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpXnwk90/fileb7e05f6d37cf}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpXnwk90/fileb7e060df376f}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpXnwk90/fileb7e0d32ccc1}
